### 2021-07-10 src/paper/results/share_known_cases.tex
Fix copy paste errors.
Add model valiadation section. Restructure results.
Improve the model fit text and add paragraphs on R_t and vaccinations.
Add section to the group specific share known cases results.

\subsection{Share of Cases that are Detected}
\label{subsec:appendix_share_known_cases}

>>>>

\subsection{Share of Detected Cases}
\label{subsec:results_share_known_cases}

We explain how we model the detection of cases in Section~\ref{sub:testing} and show the
overall share of known cases that we use as input for our testing model in
Section~\ref{subsec:data_share_known_cases}.
% 2020
Given the differential demand by symptomatic and asymptomatic individuals our model
endogenously results in group specific share known cases that are shown in
Figure~\ref{fig:share_known_cases_by_age_group}. Since older individuals are much more
likely to develop symptoms many more cases among them are detected.
% 2021
Starting in 2021 the share known cases not only depends on the overall share known cases
we feed into our model but also on the number of performed rapid tests. As more and more
(often asymptomatic and presymptomatic) individuals receive positive rapid tests and
receive confirmation, the share of detected cases starts to increase, especially after
March when rapid tests became much more widely available in Germany. This effect is very
visible for school pupils, (5-14, green line). As twice weekly rapid tests become
mandatory in schools and students start going to school after the Easter break, the share
of detected cases for that group increases drastically from 25\% to over 60\% between
April and June.
